\begin{thebibliography}{99}
\label{Bibliography}


% Change the left side page header to "Bibliography"
% This style of Bibliography is the accepted IEEE style. Change it if needed.
\bibitem{Briand.L}
Briand. L:
{\it{"Novel applications of machine learning in software testing"}},In :Proceedings of the 8th International Conference on Quality Software(QSIC), 2008, pp.3-10.
\bibitem{Xiaoyuan Xie}Xiaoyuan Xie, Joshua Ho, Christian Murphy, Gail Kaiser, Baowen Xu, Tsong Yueh Chen :
{\it{"Testing and validating machine learning classifiers by metamorphic testing"}}.In: Proceedings of the The Journal of Systems and Software  ,2011 ,pp.544-558.

\bibitem{Christian Murphy}Christian Murphy, Gail E. Kaiser, Lifeng Hu:
{\it{"Properties of machine learning applications for use in metamorphic testing"}}. In: Proceedings of the 20th International Conference on Software Engineering and Knowledge Engineering (SEKE) , 2008, pp.867-872.
\bibitem{Karl R.P.H. Leung }Karl R.P.H. Leung , W.K. Chan :
{\it{"A metamorphic testing approach for online testing of service-oriented software applications"}}.International Journal of Web Services Research ,2007,pp. 60-80.
\bibitem{Christian Murphy}Christian Murphy, Gail E. Kaiser, Kuang Shen:
{\it{"Using JML runtime assertion checking to automate metamorphic testing in applications without test oracles"}}. In: Proceedingsof 2nd International Conference on Software Testing Verification and Validation(ICST), 2009,pp. 436-445.
\bibitem {Jianqiang}Jianqiang Feng, Tsong Yueh Chen:{\it{"Metamorphic Testing of Programs on Partial Differential Equations".}}In: Proceedings of the 26 th Annual International Computer Software and Applications Conference (COMPSAC'02),2002,pp.327-333

\bibitem{Faraz Hussain }Faraz Hussain and Gary T. Leavens. :
{\it{"temporaljmlc: A JML Runtime Assertion Checker Extension for Specification and Checking of Temporal Properties"}}: Proceedings of the 8th International Conference on Software Engineering and Formal Methods, Pisa, Italy, In SEFM 2010, pp 63-72.
\bibitem{Gary T. Leavens }Gary T. Leavens, Albert L. Baker, and Clyde Ruby:
{\it{"Preliminary Design of JML: A Behavioral Interface Specification Language for Java"}}. ACM SIGSOFT Software Engineering Notes, March 2006 ,pp 1-31.
 \bibitem{Shin Yoo }Shin Yoo :
{\it{"Metamorphic testing of stochastic optimization"}}. In: Proceedings of the 3rd International Conference on Software Testing, Verification, and Validation Workshops (ICSTW),2010, pp. 192-201.
\bibitem {Tsong Yueh Chen}Tsong Yueh Chen , Joshua Ho, Christian Murphy, Gail Kaiser, Baowen Xu:
{\it{ "Fault-based testing without the need of oracles"}}. In: Proceedings of the Information and Software Technology ,2002, 923-931.

\bibitem {Xiaoyuan Xie}Xiaoyuan Xie, Joshua Ho, Christian Murphy, Gail Kaiser, Baowen Xu, Tsong Yueh Chen:
{\it{ "Application of metamorphic testing to supervised classifiers."}} In: Proceedings of the 9th International Conference on Quality Software (QSIC), pp. 135-144.

\bibitem {Tsong Yueh Chen}Tsong Yueh Chen, T.H. Tse,Zhi QuanZhou: 
{\it{"Metamorphic testing and beyond"}}. In Proceedings of the International Workshop on Software Technology and Engineering Practice (STEP), 2004, pp. 94-100.

\bibliographystyle{IEEEtranSN}  % Use the "unsrtnat" BibTeX style for formatting the Bibliography                
\bibliography{Bibliography}  % The references (bibliography) information are stored in the file named "Bibliography.bib"
\end{thebibliography}
