\documentclass[a4paper, 14pt, oneside]{Thesis}
%\usepackage{ulem}
\usepackage[square, numbers, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography

\usepackage{pslatex} %To set the font as Times New Roman
\usepackage{amsbsy} 
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{verbatim} 
\usepackage{soul}
\bibliographystyle{apa}

\usepackage{epsfig,graphics}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{subfigure}
\usepackage{tikz}
\usepackage{float}

\usepackage{graphicx}
\usepackage[export]{adjustbox}
%\usepackage{fancyhdr}
%\usepackage{lipsum}

%To have 1. instead of [1] in the bibliographic entry
\makeatletter
\renewcommand\@biblabel[1]{#1.}
\makeatother

% To remove hyphenation
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000
%
%----To make sure the page numbers are in the top middle of each page.
\fancypagestyle{Thesis}{
\fancyhf{}
\fancyhead[C]{\thepage}
\%lfoot{\thepage}
\pagestyle{fancy}
}
%redefine the plain pagestyle
%\fancypagestyle{plain}{
%\fancyhf{}
%\fancyhead[C]{\thepage}
%}
%----------------------------------------------------------------------
%% ------------------------s----------------------------------------
\input{bmacros}
\begin{document}

\frontmatter	  % Begin Roman style (i, ii, iii, iv...) page numbering


%  Title Page

\title{AUTOMATING CODE REVIEW FEEDBACK FOR STUDENT ASSIGNMENTS USING MACHINE LEARNING}
\authors  {{ RAMAKRISHNAN A M  \hspace{0.4in} 185001124\\}
{ RISHI VARDHAN K  \hspace{0.8in} 185001126\\}
{ SACHIN KRISHAN T  \hspace{0.65in} 185001128\\ } }
\addresses  { Computer Science \& Engineering\\}
\date       {\today}

\maketitle

\newpage
%% ----------------------------------------------------------------

\setstretch{1.3}
\fancyhead{}  % Clears all page headers and footers
\rhead{\thepage}  % Sets the right side header to show the page number
\lhead{}  % Clears the left side page header

\pagestyle{fancy}  % Finally, use the "fancy" page style to implement the FancyHdr headers


\Declaration{ 
%
  Certified that this project report titled
  \textbf{AUTOMATING CODE REVIEW FEEDBACK FOR STUDENT
    ASSIGNMENTS USING MACHINE LEARNING} is the \textit{bona
    fide} work of \textbf{RAMAKRISHNAN A M (185001124)},
  \textbf{RISHI VARDHAN K (185001126)}, and \textbf{SACHIN
    KRISHAN T (185001128)} who carried out the project work
  under my supervision.  Certified further that to the best
  of my knowledge the work reported herein does not form part
  of any other thesis or dissertation on the basis of which a
  degree or award was conferred on an earlier occasion on
  this or any other candidate.  \newlength{\aulength}
  \settowidth{\aulength}{SSN College of Engineering,}
  \newlength{\auclength} \settowidth{\auclength}{(HEAD OF THE
    DEPARTMENT)}

\begin{flushleft}
  \parbox[t]{\auclength}{\textbf{Dr.~T.~T.~MIRNALINEE}\\
    \textbf{HEAD OF THE DEPARTMENT}\\    
    Professor,\\
    Department of CSE,\\
    SSN College of Engineering,\\
    Kalavakkam - 603 110}
  \hfill
  \parbox[t]{\aulength}{\textbf{Dr.~R.~S.~MILTON}\\
    \textbf{SUPERVISOR}\\
    Professor,\\
    Department of CSE,\\
    SSN College of Engineering,\\
    Kalavakkam - 603 110}
\end{flushleft}
Place:\\
Date:\\

\medskip
Submitted for the examination held on\ldots\ldots\ldots\ldots
\\
\\
\\
{\bf Internal Examiner}\hfill
{\bf External Examiner}
}
\clearpage
%% Abstract in Tamil

% Acknowledgement
%\setstretch{1.3}

\clearpage
%% ----------------------------------------------------------------

% The Abstract Page

\acknowledgements{

  We would like to express our gratitude to our guide, Professor \textbf{Dr.~R.~S.~MILTON}, for his insightful ideas and suggestions, as well as his guidance, patience, and assistance in shaping and refining our work.

  We would also like to thank \textbf{Dr.~T.~T.~MIRNALINEE},
  Professor and Head of the Department of Computer Science
  and Engineering, for her invaluable support and guidance. We would like to extend our gratidue to our project
  Coordinator \textbf{Dr.~B.~Bharathi}, Associate Professor,
  for her valuable suggestions during this project.

  We also pay our respects to the founder
  \textbf{Dr.~SHIV NADAR}, Chairman, SSN Institutions. We also want to thank
  \textbf{Dr.~V.~E.~ANNAMALAI}, Principal, for all of the help provided throughout this course of study.

 We would like to express our heartfelt gratitude to all of our department's teaching and non-teaching staff members who have contributed directly or indirectly to our project work. Finally, we'd want to express our gratitude to our parents and friends for their patience, cooperation, and moral support over the years.  \newline \newline
  \newline {\bf RAMAKRISHNAN A M}\hfill {\bf RISHI VARDHAN
    K}\hfill {\bf SACHIN KRISHAN T} }
\clearpage  % Abstract ended, start a new page

\addtotoc{ABSTRACT} % Add the "Abstract" page entry to the Contents
\abstract{ \begin{spacing}{2}

    Students learning to program would benefit greatly from
    specific feedback for each program submission in order to
    enhance their programming skills. However, evaluating
    student program submissions and reviewing each one of
    them is a time consuming and tedious task for instructors
    and teaching assistants. For these reasons, we propose an
    end-to-end pipeline that automatically examines program
    design as well as its functionality to provide
    appropriate specific feedback after evaluating the
    student code submission on a scale of one to ten. Three
    regression models viz Support Vector Regressor(SVR), Random
    Forest Regressor and Multi-Layer Perceptron (MLP) Regressor
    were trained with a dataset developed from a corpus of
    480 Python programs submitted by students. In general, it
    was observed that the Random Forest Regressor performed
    better. When the program submissions are graded out of
    ten, the Random Forest Regressor model has a mean
    absolute error (MAE) of 1.7 and root mean square error
    (RMSE) of 2.3.
\end{spacing}
}
\clearpage
%%% DUMMY PAGE FOR TAMIL ABSTRACT WHICH WILL BE PRINTED SEPARATELY
%%% Since LaTeX can't print tamil characters, you've to type tamil 
%%% abstract in some other editors and print it separately. When
%%% binding the thesis place the tamil abstract in place of this blank page
%%% I'm adding this blank page for Table of Contents to point to the right page

%\pagestyle{empty}
%\newpage
%\mbox{}
%\clearpage

\pagestyle{plain}  %The page style headers have been "empty" all this time, now use the "fancy" headers as defined before to bring them back

%% ----------------------------------------------------------------
\lhead{\emph{Contents}}  % Set the left side page header to "Contents"

\tableofcontents % Write out the Table of Contents


%% ----------------------------------------------------------------
\lhead{\emph{List of Tables}}  % Set the left side page header to "List of Tables"
%\begin{spacing}{4}
%\hspace{2.5in} \textbf{List of Tables} \par 
\listoftables
%\end{spacing}

%% ----------------------------------------------------------------
\lhead{\emph{List of Figures}}  % Set the left side page header to "List if Figures"
\listoffigures  % Write out the List of Figures


%2.1 LITERATURE SURVEY OF METAMORPHIC TESTING. . . . . . . . . . . .  13


 % Write out the List of Tables


\mainmatter	  % Begin normal, numeric (1,2,3...) page numbering
\pagestyle{myheadings}  % Return the page headers back to the "fancy" style

\begin{spacing}{1.5}
%\input{chapter1} % INTRODUCTION
\input{chapter2} % LITERATURE SURVEY
\input{chapter3} % DESIGN
\input{chapter5} % IMPLEMENTATION
\input{chapter4} % CONCLUSION AND FUTURE WORK
%\input{chapter6}
\input{chapter7}
\input{chapter8}
\input{chapter9}
\input{chapter10}
\end{spacing}
\newpage
\appendix
%\addtotoc{REFERENCES}
%\input{References} 
%\bibliographystyle{plain}
%\bibliography{ref}
\begin{thebibliography}{99}
  \bibliographystyle{apa}
  
\bibitem[1]{G} ``2to3 -- Automated Python 2to3 code translation'', https://docs.python.org/3/library/2to3.html 

\bibitem[2]{F} ``AST module Python 3.10.4'', https://docs.python.org/3/library/ast.html
  
\bibitem[3]{A} Azcona D, Arora P, Hsiao I H, Smeaton
  A. (2019) ``user2code2vec: Embeddings for profiling students
  based on distributional representations of source code'' ,
  In Proceedings of the 9th International Conference on
  Learning Analytics \& Knowledge, pp. 86-95.

\bibitem[4]{O} Benjamin Paaben, Barbara Hammer, Thomas
  William Price, Tiffany Barnes, Sebastian Gross, and Niels
  Pinkwart. (2017) ``The Continuous Hint Factory-Providing
  Hints in Vast and Sparsely Populated Edit Distance Spaces'',
  arXiv preprint arXiv:1708.06564

\bibitem[5]{B} Breiman L. (2001). ``Random forests --- Machine
  Learning'' 45, 5-32.

\bibitem[6]{N} Chris Piech, Jonathan Huang, Andy Nguyen, Mike
  Phulsuksombati, Mehran Sahami, Leonidas Guibas. (2015)
  ``Learning program embeddings to propagate feedback on
  student code'' , In Proceedings of the 32nd International
  Conference on International Conference on Machine
  Learning-Volume 37. JMLR. org, 1093–1102.

\bibitem[7]{D} Drucker, Harris, et al. (1996) ``Support
  vector regression machines'', Advances in neural
  information processing systems, 9.

\bibitem[8]{H} Jović, Alan, Karla Brkic, Nikola
  Bogunovic. (2015) ``A review of feature selection methods
  with applications'' , 38th international convention on
  information and communication technology, electronics and
  microelectronics (MIPRO). Ieee, 2015.

\bibitem[9]{Q} Lili Mou, Ge Li, Lu Zhang, Tao Wang, Zhi
  Jin. (2016) ``Convolutional Neural Networks over Tree
  Structures for Programming Language Processing'', In AAAI,
  Vol. 2. 4

\bibitem[10]{M} Lili Mou, Ge Li, Yuxuan Liu, Hao Peng, Zhi
  Jin, Yan Xu, Lu Zhang. (2014) ``Building program vector
  representations for deep learning'', arXiv preprint
  arXiv:1409.3358.

\bibitem[11]{J} Maxim Rabinovich, Mitchell Stern, Dan
  Klein. (2017) ``Abstract syntax networks for code
  generation and semantic parsing'', arXiv preprint
  arXiv:1704.07535.

\bibitem[12]{L} Miltiadis Allamanis, Hao Peng, Charles
  Sutton. (2016) ``A convolutional attention network for
  extreme summarization of source code'', In International
  Conference on Machine Learning. 2091–2100.

\bibitem[13]{C} Murtagh, Fionn. (1991) ``Multilayer
  perceptrons for classification and regression''
  ,Neurocomputing 2.5-6 : 183-197.

\bibitem[14]{T}Orr, J Walker, Nathaniel Russell. (2021)
  ``Automatic Assessment of the Design Quality of Python
  Programs with Personalized Feedback'', arXiv preprint
  arXiv:2106.01399 .

\bibitem[15]{E} Pedregosa et al., (2011) ``Scikit-learn:
  Machine Learning in Python'', JMLR 12, pp. 2825-2830.

\bibitem[16]{S} Pylint.org. ``Pylint - code analysis for
  python''. https://pylint.org.

\bibitem[17]{P} Sebastian Gross, Bassam Mokbel, Benjamin
  Paaben, Barbara Hammer, Niels Pinkwart. (2014)
  ``Example-based feedback provision using structured
  solution spaces'', International Journal of Learning
  Technology 10 9, 3 , 248–280.

\bibitem[18]{R} Sebastian Proksch, Sven Amann, Sarah Nadi,
  Mira Mezini. (2016) ``A dataset of simplified syntax trees
  for C'', In Proceedings of the 13th International
  Conference on Mining Software Repositories. ACM, 476–479.

\bibitem[19]{I} Uri Alon, Meital Zilberstein, Omer Levy, Eran
  Yahav. (2018) ``A general path-based representation for
  predicting program properties'', arXiv preprint
  arXiv:1803.09544.

\bibitem[20]{K} Veselin Raychev, Martin Vechev, Eran
  Yahav. (2014). ``Code completion with statistical language
  models'',In Acm Sigplan Notices, Vol. 49. ACM, 419–428.

\end{thebibliography}


\end{document}
`
